Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-21 paper/Draft.tex
Stylized Factts section half way. Focus on uncertainty. Three sets of graphs till now. Uncertainty and other moments. IQR of uncertainty. Histogram of Uncerainty.

\begin{figure}[h]\ref{ir_popind}
	\centering
	\includegraphics[width=13cm]{figures/ir_indseni.png}
	\includegraphics[width=13cm]{figures/ir_popseni.png} \\
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

\subsection{Other Theories}

@@

\subsection{Density Estimates}

>>>>

\begin{figure}[h]\label{ir_popind}
	\centering
	\includegraphics[width=13cm]{figures/ir_indseni.png}
	\includegraphics[width=13cm]{figures/ir_popseni.png} \\
	\caption{Impulse responses of moments to a shock to inflation}
\end{figure}

\subsection{Disucussion of other theories}

@@

\subsection{Stylized Facts}

\subsubsection{Different Moments}

\begin{figure}[h]\label{UnceratitnyOtherMoments}
	\centering
	\includegraphics[width=6cm]{figures/fe_var2Q.png}
	\includegraphics[width=6cm]{figures/var_disg2Q.png}\\
	\smallskip
	\includegraphics[width=6cm]{figures/fe_var3Q.png}
	\includegraphics[width=6cm]{figures/var_disg3Q.png}\\
	\smallskip	
	\includegraphics[width=6cm]{figures/fe_var.png}
	\includegraphics[width=6cm]{figures/var_disg.png}\\
		\caption{Unceratinty and Other Moments}
\end{figure}

\begin{figure}[h]\label{IQR_Unceratitny}
	\centering
	\includegraphics[width=8cm]{figures/IQRvarCPIQ.png} \\
	\smallskip
	\includegraphics[width=8cm]{figures/IQRvarPCEQ.png}\\
		\smallskip
	\includegraphics[width=8cm]{figures/IQRvarSCEQ.png}\\
	\caption{Dispersion in Mean Forecast and Unceratinty }
\end{figure}

\begin{figure}[h]\label{Unceratitny_Histogram}
	\centering
	\includegraphics[width=6cm]{figures/PRCCPIMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCCPIVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/PRCPCEMean1_hist.png} 
	\includegraphics[width=6cm]{figures/PRCPCEVar1_hist.png}  \\
	\smallskip
		\includegraphics[width=6cm]{figures/SCEMean1_hist.png} 
	\includegraphics[width=6cm]{figures/SCEVar1_hist.png}  \\
	\caption{Distribution of Mean Forecast and Uncertainty }
\end{figure}
